Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-01-05 AO_bondedSi.tex
DTJ edits on page 8

The Si$-$Si interface gap is a low-Finesse Fabry-P\`{e}rot etalon\verb|\cite{2007fuph.book.....S}|.  The key property of an etalon is that it has a cavity enclosed between two smooth and parallel reflective surfaces where the requirements for smoothness and parallelism depend on the reflective finesse of the cavity.  For the narrow air gaps we consider here and for the modest reflectivity of a Si-vacuum interface, most gaps at Si-Si bonds will form effective etalons over most of their area.  The transmission through a Fabry-P\`{e}rot depends on the wavelength of light, the reflectivity of the etalon sidewalls, and the size of the gap.  We assume transmission is at normal incidence, the refractive index of the gap is 1.0, and the material is at $T= 295\;$K.  We compute the reflectivity for an Si$-$vacuum interface, which is a modest function of wavelength through the refractive index of Silicon, $n(\lambda, T)$ \verb|\cite{2006SPIE.6273E..77F}|, as shown in Figure \ref{figSiIndexFinesse}.  In the equations ahead we drop the subscripts on the refractive index $n(\lambda, T) \rightarrow n$ and the coefficient of finesse $F(\lambda, T) \rightarrow F$ for clarity.  The computation is simply Fresnel's law at normal incidence:

\begin{eqnarray}
R = \frac{(n-1)^2}{(n+1)^2} \\
F \equiv \frac{4R}{(1-R)^2}
\end{eqnarray}

The reflectivity is about 30\% in the wavelength range 1100 to 5000 nm.  We've defined the coefficient of finesse\verb|\cite{2007fuph.book.....S}|, $F$, a customary way to encapsulate the Fabry-P\`{e}rot etalon's dependence on the reflectivity.  The coefficient of finesse is shown in the right panel of Figure \ref{figSiIndexFinesse}.  Si is negligibly absorbing longward of about $\lambda$ = 1200 nm, which we verified by comparing the transmission of Si reference samples of different thicknesses, as shown in Figure \ref{figSiAbsorbfig}.  Figure \ref{figSiAbsorbfig} also verifies a key assumption that we will make when comparing the transmission of Si substrates of different heritage and thickness.  Specifically DSP Si pucks and wafers have the indistinguishable transmission longward of 1250 nm.  The Si refractive index is indistinguishable from sample to sample for the wavelength ranges we care about- the non-absorbing wavelengths greater than about 1200 nm.  \verb|\cite{2006SPIE.6273E..77F}| cites the wide variety of values for refractive index from the literature as evidence that batch-specific Si should be used as reference for cases in which absolute accuracy greater than $\pm5\times10^{-3}$ is desired.  An absolute deviation of $\pm5\times10^{-3}$ in refractive index corresponds to a Fresnel transmission difference of about 0.2\%, which is comparable to our measurement uncertainty.  In the next subsection we work out the wavelength dependent transmission for the air etalon.

>>>>

The Si$-$Si interface gap is a low-Finesse Fabry-P\`{e}rot etalon\verb|\cite{2007fuph.book.....S}|.  The key property of an etalon is that it has a cavity enclosed between two smooth and parallel reflective surfaces where the requirements for smoothness and parallelism depend on the reflective finesse of the cavity.  For the narrow air gaps we consider here and for the modest reflectivity of a Si-vacuum interface, most gaps at Si-Si bonds will form effective etalons over most of their area.  The transmission through a Fabry-P\`{e}rot depends on the wavelength of light, the reflectivity of the etalon sidewalls, and the size of the gap.  We assume transmission is at normal incidence, the refractive index of the gap is 1.0, and the material is at $T= 295\;$K.  We compute the reflectivity for an Si$-$vacuum interface, which is a modest function of wavelength through the refractive index of Silicon, $n(\lambda, T)$ \verb|\cite{2006SPIE.6273E..77F}|, as shown in Figure \ref{figSiIndexFinesse}.  We drop the subscripts on the refractive index $n(\lambda, T) \rightarrow n$ and the coefficient of finesse $F(\lambda, T) \rightarrow F$ for clarity.  The computation is simply Fresnel's law at normal incidence:

\begin{eqnarray}
R = \frac{(n-1)^2}{(n+1)^2} \label{Eq:FresnelR}\\
F \equiv \frac{4R}{(1-R)^2} \label{Eq:coeffF}
\end{eqnarray}

The reflectivity $R$ (Equation \ref{Eq:FresnelR}) is about 30\% in the wavelength range 1100 to 5000 nm.  We define the coefficient of finesse\verb|\cite{2007fuph.book.....S}|, $F$ (Equation \ref{Eq:coeffF}), in the customary way to encapsulate the Fabry-P\`{e}rot etalon's dependence on reflectivity.  The coefficient of finesse is shown in the right panel of Figure \ref{figSiIndexFinesse}.  Si is negligibly absorbing longward of about $\lambda$ = 1200 nm, which we verified by comparing the transmission of Si reference samples of different thicknesses, as shown in Figure \ref{figSiAbsorbfig}.  Figure \ref{figSiAbsorbfig} also verifies a key assumption that we will make when comparing the transmission of Si substrates of different heritage and thickness.  Specifically DSP Si pucks and wafers have the indistinguishable transmission longward of 1250 nm.  The Si refractive index is indistinguishable from sample to sample for the wavelength ranges we care about- the non-absorbing wavelengths greater than about 1200 nm.  \verb|\cite{2006SPIE.6273E..77F}| cites the wide variety of values for refractive index from the literature as evidence that batch-specific Si should be used as reference for cases in which absolute accuracy greater than $\pm5\times10^{-3}$ is desired.  An absolute deviation of $\pm5\times10^{-3}$ in refractive index corresponds to a Fresnel transmission difference of about 0.2\%, which is comparable to our measurement uncertainty.  In the next subsection we work out the wavelength dependent transmission for the air etalon.
